Latex Tikz Test, Linear Equation Plotting, Linear Spline

### 2019-12-09 _other/tikz/fplot/functionplot.tex
tikz example for relative positioning

@@

%%%%%%%%%%%%%%%%%%%%%
%%% Draw Lines
%%%%%%%%%%%%%%%%%%%%%
\begin{multicols}{3}
[
\section{Tikz Four Lines}
Draw four lines, sum them up linear spline, then invert
]

>>>>

% Titling and Author
\title{Latex Tikz Test, Linear Equation Plotting, Linear Spline}
\author{\href{https://fanwangecon.github.io/}{Fan Wang}\thanks{https://fanwangecon.github.io, repository: \href{https://fanwangecon.github.io/Tex4Econ/}{Tex4Econ}}}
\date{\today}

@@

%%%%%%%%%%%%%%%%%%%%%
%%% Draw Lines
%%%%%%%%%%%%%%%%%%%%%
\begin{multicols}{3}
[
\section{Tikz Four Lines}
Draw four lines, sum them up linear spline, then invert. A3 page has 29.7 cm width. Below, width is 7 cm for each plot, so 21 cm all together generally. Margins are 1 inch on each side, so about 5 cm together. 
]
